Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 3

    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
    the accreted component), and compare with the relation between \mstar{} and 
    accreted fraction derived from the Illustris simulation 
    (\citealt{RodriguezGomez2016}). 
    It is intriguing to see that, our proxy of accreted mass not only strongly 
    correlates with \mtot{}, the relation is surprisingly consistent with the 
    prediction from \citet{RodriguezGomez2016}. 
    Given the different definition of total stellar mass,

@@

    To see whether \minn{} can reasonably represent the \textit{in-situ} mass, we 
    compare the average \mden{} profiles of HSC massive galaxies in two \mtot{} 
    bins (Left panel of Fig \ref{fig:discussion_1}, 
    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:

>>>>

    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
    the accreted component), and compare with the relation between \mstar{} and 
    accreted fraction derived from the Illustris simulation 
    (\citealt{RodriguezGomez2016}). 
    It is intriguing to see that, our proxy of accreted mass not only strongly 
    correlates with \mtot{}, the relation is surprisingly consistent with the 
    prediction from \citet{RodriguezGomez2016}. 
    Given the limitations of the Illustris simulation and the different definitions
    of total stellar mass, the almost perfect consistency may well be a coincidence. 
    However, it is encouraging to see that our arbitrary choices of aperture masses 
    can already reproduce similar slope and scatter of this relation. 
    Right now, there are other hydrodynamic simulations that predict significantly 
    different mass fraction of accreted stars at fixed \mstar{} (e.g. 
    \citealt{Lackner2012, Qu2017}). 
    Therefore, it will be very useful to perform more detailed comparisons with 
    these simulations and explore the possibilities of using certain aperture mass 
    to trace the \textit{in-situ} component.

@@

    To further check whether \minn{} can reasonably represent the \textit{in-situ} 
    mass, we compare the average \mden{} profiles of HSC massive galaxies in two 
    \mtot{} bins (Left panel of Fig \ref{fig:discussion_1}, 
    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:
